RJObject Paper

### 2014-06-14 Documents/Paper/ms.tex
More talk about sinusoids

\section{Sinusoidal Example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different frequencies and amplitudes.
This kind of model has many applications\citep[see e.g.][]{bretthorst}.

>>>>

\section{Sinusoidal Example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications\citep[see e.g.][]{bretthorst}.
